### 2021-02-15 text/main.tex
tex structure

Machine indexing of institutional repositories: indexing Edoc with Annif
and BARTOC FAST as proof of concept

@@

The third and final constraint takes into account the possibility of
having to extend the prototype to the complete Edoc data. On the one
hand, the sample data set should be small enough to allow for easy
handling and rapid iteration. On the other hand, the sample data set
should not be trivial but reflect the quirks and inadequacies of the
complete dataset. In other words, we are looking for an abstraction
rather than an idealization in the sense of @Stokhof.2011.

@@

The first constraint is that each item in the sample data set needs to
have a text. Intuitively, this text could consist of a title, an
abstract, or even a full text, or any combination of the above. Similar
to manual indexing, having more information (that is, longer texts)
usually implies a higher indexing quality in machine indexing. However,
this assumption needs to be confirmed empirically for the given machine
indexing framework and data set. If indeed confirmed, it might be
advisable only to index items that have a certain minimal text length.
Therefore, in order to construct the sample data set, we require each
item to have a non-empty value in the data fields \texttt{title},
\texttt{abstract}, and \texttt{id\_number} as proxy to retrieve a full
text remotely. Note that even more context could be provided by taking
into account other data fields such as \texttt{type},
\texttt{publication} or \texttt{department}. Especially the latter might
be valuable when disambiguating homonymous or polysemous words. For
example, consider the item
\texttt{https://edoc.unibas.ch/id/eprint/76510} which is titled
``Blacking Out''. Without further context, this title could refer
(amongst others) to a physiological phenomenon, a sudden loss of
electricity, or a measure taken in wartime. Knowing that the item was
published by a researcher employed by the Faculty of Business and
Economics (and not, say, by the Faculty of Medicine) gives us reason to
exclude the first meaning. However, this idea cannot be implemented with
the out of the box instance of Annif employed in this chapter (see
\protect\hyperlink{machine-indexing}{subsection ``Machine indexing''}).

@@

In order to determine how well the sample data set represents the raw
Edoc data, a one-sample chi-square test was conducted on each selection
data field {[}see @Parke.2013, chapter 1{]}. The results indicate that
the sample data proportions of items are significantly different from
the raw Edoc data per department (see Figure 1 for more details).

@@

The most common approach for assessing the output of machine indexing is
by systematically comparing it with a gold standard (sometimes also
referred to as model or reference). @Golub.2016 {[}p. 10{]} define a
gold standard as ``a collection in which each document is assigned a set
of subjects that is assumed to be complete and correct'' where
``\emph{complete} means that all subjects that should be assigned to a
document are in fact assigned, and \emph{correct} means that there are
no subjects assigned that are irrelevant to the content''. Put
inversely, if an item in the gold standard lacks subject terms
describing its content, the assignment is not complete; and if an item
in the gold standard has been assigned subject terms that are not
relevant to its content, the assignment is not correct.

A gold standard is usually the product of manual indexing by
``information experts, subject experts, or potential or real end users''
{[}@Golub.2016, p. 10{]}. This entails its own host of epistemic
problems relating to objectivity and consistency of the assigned subject
terms. Most importantly, however, the construction of a gold standard
from scratch is very expensive. It is therefore not an option for the
project at hand. Rather, I will construct what could be called
derivative gold standards by reusing indexing data that is already
available. Here we can distinguish two distinct kinds of derivative gold
standards: first, I will construct a derivative gold standard based on
the author keywords available in the sample data set; call this the
``native'' gold standard. Second, I will construct a derivative gold
standard based on indexing metadata available in repositories distinct
from Edoc; call this the ``foreign'' gold standard.

There are other methods for assessing machine indexing quality besides
comparison with a gold standard that are worth mentioning. These include
an evaluation in the context of indexing workflows {[}@Golub.2016, p.
13ff.{]}, the assessment of retrieval performance {[}@Golub.2016, p.
15-23.{]}, and so-called model free assessments {[}@Louis.2013{]}.

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\newenvironment{Shaded}{}{}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

% ORCID
\usepackage{scalerel}
\usepackage{tikz}
\usetikzlibrary{svg.path}

\definecolor{orcidlogocol}{HTML}{A6CE39}
\tikzset{
	orcidlogo/.pic={
		\fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
		\fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
		svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
		svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
	}
}

\newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
				\begin{tikzpicture}[yscale=-1,transform shape]
					\pic{orcidlogo};
				\end{tikzpicture}
			}{|}}}}

\author{}
\date{}

\begin{document}

\input{./titlepage/titlepage}
\newpage

\input{./abstract/abstract}
\newpage

{
\setcounter{tocdepth}{3}
\tableofcontents
}

@@

The third and final constraint takes into account the possibility of
having to extend the prototype to the complete Edoc data. On the one
hand, the sample data set should be small enough to allow for easy
handling and rapid iteration. On the other hand, the sample data set
should not be trivial but reflect the quirks and inadequacies of the
complete dataset. In other words, we are looking for an abstraction
rather than an idealization in the sense of Stokhof and van Lambalgen
(2011).

@@

The first constraint is that each item in the sample data set needs to
have a text. Intuitively, this text could consist of a title, an
abstract, or even a full text, or any combination of the above. Similar
to manual indexing, having more information (that is, longer texts)
usually implies a higher indexing quality in machine indexing. However,
this assumption needs to be confirmed empirically for the given machine
indexing framework and data set. If indeed confirmed, it might be
advisable only to index items that have a certain minimal text length.
Therefore, in order to construct the sample data set, we require each
item to have a non-empty value in the data fields \texttt{title},
\texttt{abstract}, and \texttt{id\_number} as proxy to retrieve a full
text remotely. Note that even more context could be provided by taking
into account other data fields such as \texttt{type},
\texttt{publication} or \texttt{department}. Especially the latter might
be valuable when disambiguating homonymous or polysemous words. For
example, consider the item
\texttt{https://edoc.unibas.ch/id/eprint/76510} which is titled
``Blacking Out.'' Without further context, this title could refer
(amongst others) to a physiological phenomenon, a sudden loss of
electricity, or a measure taken in wartime. Knowing that the item was
published by a researcher employed by the Faculty of Business and
Economics (and not, say, by the Faculty of Medicine) gives us reason to
exclude the first meaning. However, this idea cannot be implemented with
the out of the box instance of Annif employed in this chapter (see
\protect\hyperlink{machine-indexing}{subsection ``Machine indexing''}).

@@

In order to determine how well the sample data set represents the raw
Edoc data, a one-sample chi-square test was conducted on each selection
data field (see Parke 2013, chap. 1). The results indicate that the
sample data proportions of items are significantly different from the
raw Edoc data per department (see Figure 1 for more details).

@@

The most common approach for assessing the output of machine indexing is
by systematically comparing it with a gold standard (sometimes also
referred to as model or reference). Golub et al. (2016, 10) define a
gold standard as ``a collection in which each document is assigned a set
of subjects that is assumed to be complete and correct'' where
``\emph{complete} means that all subjects that should be assigned to a
document are in fact assigned, and \emph{correct} means that there are
no subjects assigned that are irrelevant to the content.'' Put
inversely, if an item in the gold standard lacks subject terms
describing its content, the assignment is not complete; and if an item
in the gold standard has been assigned subject terms that are not
relevant to its content, the assignment is not correct.

A gold standard is usually the product of manual indexing by
``information experts, subject experts, or potential or real end users''
(Golub et al. 2016, 10). This entails its own host of epistemic problems
relating to objectivity and consistency of the assigned subject terms.
Most importantly, however, the construction of a gold standard from
scratch is very expensive. It is therefore not an option for the project
at hand. Rather, I will construct what could be called derivative gold
standards by reusing indexing data that is already available. Here we
can distinguish two distinct kinds of derivative gold standards: first,
I will construct a derivative gold standard based on the author keywords
available in the sample data set; call this the ``native'' gold
standard. Second, I will construct a derivative gold standard based on
indexing metadata available in repositories distinct from Edoc; call
this the ``foreign'' gold standard.

There are other methods for assessing machine indexing quality besides
comparison with a gold standard that are worth mentioning. These include
an evaluation in the context of indexing workflows (Golub et al. 2016,
13ff.), the assessment of retrieval performance (Golub et al. 2016,
15--23.), and so-called model free assessments (Louis and Nenkova 2013).

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Golub.2016}{}%
Golub, Koraljka, Dagobert Soergel, George Buchanan, Douglas Tudhope,
Marianne Lykke, and Debra Hiom. 2016. {``A Framework for Evaluating
Automatic Indexing or Classification in the Context of Retrieval.''}
\emph{Journal of the Association for Information Science and Technology}
67 (1): 3--16. \url{https://doi.org/10.1002/asi.23600}.

\leavevmode\hypertarget{ref-Louis.2013}{}%
Louis, Annie, and Ani Nenkova. 2013. {``Automatically Assessing Machine
Summary Content Without a Gold Standard.''} \emph{Computational
Linguistics} 39 (2): 267--300.
\url{https://doi.org/10.1162/COLI\%7B/textunderscore\%20\%7Da\%7B/textunderscore\%20\%7D00123}.

\leavevmode\hypertarget{ref-Parke.2013}{}%
Parke, Carol. 2013. \emph{Essential First Steps to Data Analysis:
Scenario-Based Examples Using SPSS}. Thousand Oaks: {SAGE Publications}.
\url{https://doi.org/10.4135/9781506335148}.

\leavevmode\hypertarget{ref-Stokhof.2011}{}%
Stokhof, Martin, and Michiel van Lambalgen. 2011. {``Abstractions and
Idealisations: The Construction of Modern Linguistics.''}
\emph{Theoretical Linguistics} 37 (1-2): 1--26.
\url{https://doi.org/10.1515/thli.2011.001}.

\end{CSLReferences}

\end{document}
